\Large\bf Scalable and Probabilistic Leaderless BFT Consensus through Metastability

### 2020-11-07 paper_fr.tex
S5 - avalanche_fr.tex terminé

\section{Peer-to-Peer Payment System}
\label{sec:implementation}

@@

%O Using Snowball consensus, we have implemented a bare-bones payment system, Avalanche, which supports Bitcoin transactions. In this section, we describe the design and sketch how the implementation can support the value transfer primitive at the center of cryptocurrencies.
Grâce au consensus Snowball, nous avons implémenté un système de paiement simpliste, Avalanche, qui supporte les transactions Bitcoin. Dans cette section, nous en décrivons la conception et schématison la manière donc l'implémentation peut supporter la primitive de transfert de valeur au centre des cryptomonnaies.
%O Deploying a full cryptocurrency involves bootstrapping, minting, staking, unstaking,
%O and inflation control. While we have solutions for these issues, their full
%O discussion is beyond the scope of this paper, whose focus is centered on the
%O novel Snow consensus protocol family.
Le déploiement complet d'une cryptomonnaie implique l'initialisation, l'émission, le dépôt, le retrait et le contrôle de l'inflation. Nous disposons de solutions à ces problèmes mais leur description détaillée sort du cadre de cet article, dont l'objet est la nouvelle famille de consensus Snow. % HOULA staking unstaking
%In this section,
%we focus on how Avalanche can support the value transfer primitive at the center of cryptocurrencies.
%\paragraph{XXX: the original implementation paragraph in Model}

>>>>

\section{Système de paiement pair à pair}
\label{sec:implementation}

@@

%O Using Snowball consensus, we have implemented a bare-bones payment system, Avalanche, which supports Bitcoin transactions. In this section, we describe the design and sketch how the implementation can support the value transfer primitive at the center of cryptocurrencies.
Grâce au consensus Snowball, nous avons implémenté un système de paiement simpliste, Avalanche, qui supporte les transactions Bitcoin. Dans cette section, nous en décrivons la conception et schématison la manière dont l'implémentation peut supporter la primitive de transfert de valeur au cœur des cryptomonnaies.
%O Deploying a full cryptocurrency involves bootstrapping, minting, staking, unstaking,
%O and inflation control. While we have solutions for these issues, their full
%O discussion is beyond the scope of this paper, whose focus is centered on the
%O novel Snow consensus protocol family.
Le déploiement complet d'une cryptomonnaie implique l'initialisation, l'émission, le dépôt, le retrait et le contrôle de l'inflation. Nous disposons de solutions à ces problèmes mais leur description détaillée sort du cadre de cet article, dont l'objet est la nouvelle famille de consensus Snow. % HOULA staking unstaking
%In this section,
%we focus on how Avalanche can support the value transfer primitive at the center of cryptocurrencies.
%\paragraph{XXX: the original implementation paragraph in Model}
